<<<<<<< HEAD
---
title: "Financial Engineering and TensorFlow"
author: "Joocheol Kim"
date: "`r Sys.Date()`"
output:
  bookdown::gitbook
site: bookdown::bookdown_site
documentclass: book
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview {-}

금융공학, 인공지능. 두가지 모두 매력적인 말입니다.

이 두가지를 모두 배울 수 있을까요? 그것이 바로 이 강의가 추구하는 바입니다. 금융공학과 인공지능의 기초뿐만이 아니라, 수준 있는 내용까지 모두 배우고 이를 세상에 활용해 볼 수 있을 정도까지의 준비를 하는 것입니다.

이 강의는 아직도 개발 중입니다. 계속해서 새로운 내용을 추가하도록 하겠습니다.

=======
--- 
title: "Financial Engineering and TensorFlow"
author: "Joocheol Kim"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
>>>>>>> ff44df25becc0c008f6b346d81b26b8e8f4890ed
